Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-05-20 GWLDCII.tex
read up to 4.4

\begin{cor}\label{no coloops}
Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
\end{cor}
\begin{proof}
For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order and so by Lemma~\ref{lem no fourth vertex} there can be no propagator $p$ with $I_{i}(p) = i-1$. Thus $i-1 \not\in I_{i}$, so $i-1$ is not a coloop. Since this holds for any $i \in [n]$, the Grassmann necklace admis no coloops.

@@

\begin{proof}
  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices as appropriate), and incrementing all indices greater than $i$ in each Grassmann necklace element.  Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
  \[
  I_j^{W} =
  \begin{cases}
    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
  \end{cases}
  \]

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
  \end{itemize}
\end{lem}

@@

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.

>>>>

\begin{cor}\label{no coloops}\sanote{cite more prominently in frontmatter}
Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
\end{cor}
\begin{proof}
For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order and so by Lemma~\ref{lem no fourth vertex} there can be no propagator $p$ with $I_{i}(p) = i-1$. Thus $i-1 \not\in I_{i}$, so $i-1$ is not a coloop. Since this holds for any $i \in [n]$, the Grassmann necklace admis no coloops.

@@

\begin{proof}
  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$) \sanote{changed a bit of wording on the proof}, and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.  Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
  \[
  I_j^{W} =
  \begin{cases}
    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
  \end{cases}
  \]

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator \hlfix{$q = (i, j)$ with no other propagators inside $q$ in the $<_i$ ordering, and $j <_1 i$.}{changed. Correct? Explicitly, not letting $i <_i j <_i n-1$. Also made this change below. } 
  \end{itemize}
\end{lem}

@@

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators \hlfix{$p = (n-3, n-1)$ and $q= (n-5, n-3)$}{changed. correct?} (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.
